On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2022-10-24 manuscript/manuscript.tex
smoothed intro

\begin{abstract}
The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit
tests for comparing a sample with a hypothesized parametric distribution.
Nevertheless, it has often been misused. The standard one-sample KS test applies
to independent, continuous data with a hypothesized distribution that is
completely specified. It is not uncommon, however, to see in the literature that
it was applied to dependent, discrete, or rounded data, with hypothesized
distributions containing estimated parameters. For example, it has been
``discovered'' multiple times that the test is too conservative when
hypothesized distribution has parameters that need to be estimated.
We demonstrate misuses of the one-sample KS test in
three scenarios through simulation studies:
1) the hypothesized distribution has unspecified parameters;
2) the data are serially dependent; and
3) a combination of the first two scenarios.
For each scenario, we provide remedies for practical applications.

\bigskip
\noindent\sc{Keywords}:
nonparametric bootstrap;
parametric bootstrap;
\end{abstract}

@@

The standard KS test is not applicable when the hypothesized distribution
contains fitted parameters. \citet{Steinskog} ``discovers'' the change in power
when using estimated parameters and stresses caution in using the KS test in
such ways. In fact, \citet{Lilliefors} shows for the normal distribution that using the
standard table when values of the mean and standard deviation are estimated
yields extremely conservative results.
% JY: this paper set up a wrong target; they didn't even cite bootstrap!
% This is supported by \citet{Capasso},
% who concludes that failing to re-estimate the parameters may lead to wrong,
% overly-conservative approximations to the distributions of goodness-of-fit test
% statistics based on the empirical distribution function. \citet{Capasso} also
% notes that the impact of this mistake may turn out to be dramatic and does not
% vanish as the sample size increases.
This problem can be solved by parametric bootstrap \citep{Efron}, where
bootstrap samples of the testing statistics are constructed from samples
generated from the fitted hypothesized distribution. A nonparametric bootstrap
solution is not trivial because the a nonparametric bootstrap sample of the
observed data have ties, which would not happen for continuous distribution.
A nonparametric remedy was provided by \citet{Babu}, who derived the bias and
showed how to correct it. They further noted that both parametric and
non-parametric procedures lead to correct asymptotic levels.
% JY: Genest at al is not about our setting. \citet{Genest} provides
% validity for using parametric bootstrap with various goodness-of-fit tests.

The standard KS test does not apply to serially dependent data either. For
testing normality, \citet{Durilleul} demonstrated that a naive application of
the KS statistic is too liberal for medium-to-high positive serieal dependence,
and that for negative dependence, the behavior is asymmetrical. For remedies,
\citet{Weiss} provides a procedure that is applicable specifically for data
modeled by the second-order auto-regressive (AR) process where the AR parameters
are known. \citet{Lanzante} tests various strategies for dealing with temporal
dependence and concludes that a test based on Monte-Carlo simulations performed
the best. \jy{need some sentences to elaborate the issue and identify a gap in
  the literature.}

@@

\end{document}

>>>>

\begin{abstract}
The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit
tests for comparing a sample with a hypothesized continuous distribution.
Nevertheless, it has often been misused. The standard one-sample KS test applies
to independent, continuous data with a hypothesized distribution that is
completely specified. It is not uncommon, however, to see in the literature that
it was applied to dependent, discrete, or rounded data, with hypothesized
distributions containing estimated parameters. For example, it has been
``discovered'' multiple times that the test is too conservative when
hypothesized distribution has parameters that need to be estimated.
We demonstrate misuses of the one-sample KS test in
three scenarios through simulation studies:
1) the hypothesized distribution has unspecified parameters;
2) the data are serially dependent; and
3) a combination of the first two scenarios.
For each scenario, we provide remedies for practical applications.

\bigskip
\noindent{\sc Keywords}:
nonparametric bootstrap;
parametric bootstrap.
\end{abstract}

@@

When the hypothesized distribution contains fitted parameters, as is the case in
most goodness-of-fit test settings, the standard KS test is not applicable.
\citet{Steinskog} ``discovers'' the change in power
when using fitted parameters and stresses caution in using the KS test in
such ways. In fact, using fitted parameters in place of the true parameters in
KS test is long known to yield extremely conservative results
\citep[e.g.,][]{Lilliefors}. This problem can be solved by parametric
bootstrap \citep{efron1985bootstrap, hall1991two}, where
bootstrap samples of the testing statistics are constructed from samples
generated from the fitted hypothesized distribution. A nonparametric bootstrap
solution is not trivial because the a nonparametric bootstrap sample of the
observed data have ties, which would not happen for continuous distributions.
\citet{Babu} derived the bias of standard nonparametric bootstrap and
showed how to correct it. They further noted that both parametric and
non-parametric procedures lead to correct asymptotic levels.

The standard KS test does not apply to serially dependent data either. The
distribution of the KS statistic would have a higher variance for positively
dependent data than that derived when the data are independent because of a
smaller effective sample size. For example, for
testing normality, \citet{Durilleul} demonstrates that a naive application of
the KS statistic is too liberal for medium-to-high positive serieal dependence,
and that for negative dependence, the behavior is asymmetrical. For remedies,
\citet{Weiss} provides a procedure that is applicable specifically for data
modeled by the second-order auto-regressive (AR) process where the AR parameters
are known. \citet{Lanzante} tests various strategies for dealing with temporal
dependence and concludes that a test based on Monte-Carlo simulations performed
the best. When additionally the hypothesized distribution contains unknown
parameters, the standard KS test becomes even further inapplicable.

@@

\end{document}
%%% LocalWords: 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% ispell-personal-dictionary: ".aspell.en.pws"
%%% fill-column: 80
%%% eval: (auto-fill-mode 1)
%%% End:
